model4you reproducing: Individual treatment effect prediction for amyotrophic

### 2018-01-10 pkg/model4you/inst/reproducing_papers/2017_individual_treatment_effect_als_smmr.Rmd
finish reproducing papers
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1936 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 536dba33ea2da730ec3044df21a3de516be0d3c2

---
title: "model4you reproducing: Individual treatment effect prediction for amyotrophic lateral sclerosis patients"
author: "Heidi Seibold"
date: "December 22, 2017"
output: html_document
---

@@

## dependence plot
```{r}
dp_alsfrs <- cbind(pm_alsfrs, ALSFRSdata)

dp_plot_alsfrs <- function(var) {
  print(ggplot(dp_alsfrs, aes_string(y = "RiluzoleYes", x = var)) +
    geom_point() + geom_smooth(se = FALSE))
}
dp_plot_alsfrs("time_onset_treatment")
dp_plot_alsfrs("value_creatinine")
dp_plot_alsfrs("value_phosphorus")
dp_plot_alsfrs("subjectliters_fvc")
```

>>>>

---
title: 'model4you reproducing: Individual treatment effect prediction for amyotrophic
  lateral sclerosis patients'
author: "Heidi Seibold"
date: "December 22, 2017"
output:
  pdf_document: default
  html_document: default
---

@@

## dependence plot
```{r}
dp_plot <- function(var, data) {
  p <- ggplot(data, aes_string(y = "RiluzoleYes", x = var))

  if(is.factor(data[, var])) {
    p <- p + geom_boxplot()
  } else {
    p <- p + geom_point() + geom_smooth(se = FALSE)
  }

  print(p)
}

dp_alsfrs <- cbind(pm_alsfrs, ALSFRSdata)

dp_plot("time_onset_treatment", dp_alsfrs)
dp_plot("value_creatinine", dp_alsfrs)
dp_plot("value_phosphorus", dp_alsfrs)
dp_plot("subjectliters_fvc", dp_alsfrs)

dp_alssurv <- cbind(pm_alssurv, ALSsurvdata)

dp_plot("age", dp_alssurv)
dp_plot("time_onset_treatment", dp_alssurv)
dp_plot("weakness", dp_alssurv)
dp_plot("height", dp_alssurv)

```
